%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}

This work was supported by the NSA National Information Assurance Lab and by the Institute of Computing, Information and Cognitive Systems (ICICS) at the University of British Columbia, Vancouver Campus.

I would like to thank Dr. Ivan Beschastnikh for all his help and guidance throughout the entirety of this project and giving me the courage and inspiration to persevere even when I was ready to hang up my boots. I would also like to thank Prof. Margo Seltzer for giving me valuable feedback and agreeing to be my second reader. More than that, I am eternally grateful to Prof. Seltzer for being the beacon of hope during my time at UBC, and for all her advise, kindness, and warmth. 

This work would not have been possible had it not been for Dr. Ali Razeen. The time and energy he spent on this project and in guiding me through the maze of academic publishing has made me develop a deeper understanding and appreciation towards the process. His optimism perfectly balances his scepticism (which a security researcher has oodles of) and gave me the much needed confidence to keep calm and carry on.

I would also like to thank all the members of NSS lab who were with me along this journey through graduate school: Amanda Levin (n\'ee Carbonari), Clement Fung, Fabian Ruffy, Adam Geller, Vaastav Anand, Surbhi Palande, Nodir Kodirov, and Anthony Mason. I am eternally grateful for all the support and making my time at UBC incredibly fun. 

In addition to my friends mentioned above, I would also like to thank all my friends at UBC: Hayley Guillou, Anna Scholtz, Giovanni Viviani, Nico Ritschel, Aarti Kashyap, Syed Mubashir Iqbal, and many others who deserve to be listed. You have kept me sane and going when my research was not, and helped me keep some form of work-life balance. 

Lastly, I must thank my family and friends. Three different time-zones and the great physical distance between us never came in the way of your unconditional and complete support of this path I have embarked upon. I am extremely grateful and blessed to have you all on my side.  