\chapter{Limitations}
\label{sec:limitations}

Now we turn to discuss the design limitations of Trusted Capsules. In this section, we cover the limitations imposed by our design choices and the
limitations imposed by the specific choice of software and hardware. Then later on, in Chapter \ref{ch:unmodified_app}, we take a gander at why Trusted Capsules remains a rather naive attempt at
solving the problem of retrofitting existing applications with security
extensions.

\section{Design Limitations}
\begin{enumerate}
    \item {\bf Inability to limit trust in optimistic state}: In the optimistic
state, we trust the normal world kernel, the app, and the user, to not leak
capsule data to unauthorized apps. Such trust may not be warranted even in a
non-adversarial setting. For example, an app might create temporary copies of
the files it has opened into a world-readable directory or the user might copy
the data into the system clipboard. While we may use techniques such as
information flow control to detect such data leaks, doing so would dramatically reduce performance.

    \item {\bf Lack of app semantics}: Since we interpose only on the {\tt
    open()} and {\tt close()} syscalls to execute policies, a policy may not
    reason about {\em why} an app is opening a file. For example, when a user opens a document in a  \texttt{vim}, \texttt{vim} opens the document, creates a swap file, copies the contents of the document to the swap file, and then closes the document. All subsequent reads and writes are done to the swap file thereafter. On close, the original file is opened again, the contents of the swap file are copied back to the main document, and the main file is closed and the swap file deleted. 
    
    Hence, while from a user's perspective, the capsule was opened once and closed once, the policy would observe multiple capsule access attempts. This makes it difficult to identify the legitimate accesses from the application quirks. The data monitor handles Policies that rely on access logs have to be aware of this disconnect.

    \item {\bf Abusive policies}: Although we run capsule policies in a sandbox,
we do not completely prevent all damage a malicious policy can inflict. It can,
for example, access a user's GPS data and send them to a server to track her whereabouts. To handle this limitation, we either need some
systematic way of vetting the data a policy sends to a remote server or prevent
it from sending device data altogether.

    \item{\bf Trusting actions from untrusted OS}: In our design, the signal
    ({\tt open()} and {\tt close()} ) to the TEE to decrypt a capsule originates in the untrusted part of the system. The TEE cannot differentiate between genuine access and similar access requested by a malicious application.
    
    Trusting the actions originating in the normal world dilutes the guarantees we make about the transition from the pessimistic state to the optimistic state of our threat model. Moreover, trusting the normal world invalidates
    the need to use a TEE for secure processing of a Trusted Capsule.
    
\end{enumerate}

\section{Prototype Limitations:}
In this section, we list the limitations that bound the current prototype from
realizing the full vision of the Trusted Capsule model of data protection. Here
we note some design and implementation limitations.

\begin{enumerate}
    \item FUSE can be used interpose on only the file I/O system calls that are
directed to a FUSE serviced mount point. This poses some challenges in making
Trusted Capsules work seamlessly with an unmodified application.\\There is no
way for the FUSE filesystem code to identify when a process that had been
issuing IO to the mount point dies. The implication of this fact for the
prototype is that there is no good and atomic way to delete the shadow file on
the termination of the process. The prototype handles this by setting up a
background process that monitors if the process that had accessed the mount point
has terminated.
    \item The stock configuration for the TrustZone memory partitions makes the
Secure World a very memory-constrained environment. The memory that is available
in the secure world is only 10 MB, and that needs to host the Secure OS as well
as any trusted application code that must run in Trustzone. Linaro OP-TEE
recently included dynamic shared memory in their Secure OS, but to access those
features, one has to have a higher kernel version than what gets shipped with
the stock Debian OS rootfs image. More recent Linux kernel versions have known
problems with the HDMI drivers, which causes the Linux kernel to panic when a
monitor is plugged in.

This limitation hits our prototype particularly badly. In the current prototype,
we send a copy of the entire file to TrustZone to decrypt. Since there are
severe restrictions on the amount of memory available in TrustZone, we are
unwittingly bounded on the maximum file size that can be processed as a capsule.
    \item The implementation has a limitation that it needs to create copies of
the data buffers to process each part of the capsule. This creates more memory
pressure in an already resource-constrained environment.

\item The Policy API is currently limited to policies that require access to local time and the GPS coordinates (ideally, the GPS driver should run in the TEE OS). To support policies that rely on other signals and/or sensors will require adding the device driver, writing the interfacing code in the trusted application, and updating the Lua-to-C bindings. This is a well-defined albeit convoluted workflow that makes it harder to make the policy language more flexible.


\end{enumerate}

